\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Willem,
    middleinitial=N,
    lastname=Elsdon,
    email=willelsdon@gmail.com,
    phone=909-202-3855,
    linkedin=willem-elsdon,
    github=welsdon,
    city=Boise,
    state=Idaho
]

\vspace{0.05in}
\emph{\today}
\vspace{0.15in}


To whom it may concern:

I'm a Systems Engineer II with an active TS/SCI clearance and over 3 years of experience in Software
Quality Assurance within the Defense and Space industries. As a member
of multiple warfighter focused programs, I know that
the skills and experience I posses can be of great value to High Point
Aerotechnologies in a Quality Assurance role. I understand that this
role is more hardware focused, but I believe my previous experience
below proves that regardless of application I can and will contribute to
the overall goal of the company and the C-UxS program.

I've worked on the F-35 Joint Strike Fighter $($JSF$)$ for Northrop
Grumman as a composite design engineer, responsible for the analysis and
repair of
Out of Tolerance $($OOT$)$ air inlet ducts. Repair included detailed
patch work designed using CATIA V5 and FiberSim. I then created reports
for use by Liaison engineers who would then implement those patches.

While I attended BSU I was a mechanical engineering intern working for
Western Aircraft, a relatively small upgrade and repair facility for
private aircraft within the Treasure Valley $($you may have seen their
refueling trucks at the Boise airport$)$. I was responsible for
adding and replacing suites of avionics while verifying no regression in
design occurred. This was all achieved using SolidWorks. I grew to
appreciate the small scale of Western Aircraft, as we could fail fast if necessary.
And I can't forget to mention the friends I made while working with a team that small.
It was a great experience and I hope to be able to enjoy a similar
feeling of comradery at High Point Aerotechnologies.

After earning my Bachelor of Science in Mechanical Engineering from
Boise State University in 2020 I was hired by Raytheon, specifically the
Intelligence \& Space division. From then on I've been primarily focused
on system level integration, verification, and testing of both legacy
and prototype programs.

Thank you for taking the time to review my application. I look forward
to hopefully meeting with you in the future to further discuss my
qualifications for a position as a Quality Engineer at High Point Aerotechnologies.
If you have any questions, please feel free to
email me at \href{mailto:willelsdon@gmail.com}{willelsdon@gmail.com} or
call me at \href{tel:+1-909-202-3855}{909-202-3855}.

Sincerely,

\vspace{0.15in}

Willem Elsdon

\end{document}