\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Willem,
    middleinitial=N,
    lastname=Elsdon,
    email=willelsdon@gmail.com,
    phone=909-202-3855,
    linkedin=willem-elsdon,
    github=welsdon,
    city=Boise,
    state=Idaho
]

\vspace{0.05in}
\emph{\today}
\vspace{0.15in}


To whom it may concern:

I'm a Systems Engineer II with an active TS/SCI clearance and over 3 years of experience in Software
Quality Assurance within the Defense and Space industries. I understand that this
role is slightly outside of what my current and past work entails. However, I
believe my experience proves that regardless of application I can and will contribute to
the goals of Micron Technology and the DRAM engineering group.

For over three years I've been in some way testing large systems.
Whether it be manually running Day In the Life $($DiTL$)$ tests or
writing Gherkin for new automated test procedures. I've been involved in
all areas of Integration, Verification, and Test. I've learned to
troubleshoot using various methods on multiple systems and have helped
others do the same. I've also been tasked with restructuring and
improving an MBSE model that has since been customer approved. All of which I never went to college for. I thought
for sure I'd be designing aircraft and their components in CAD but I
haven't, not even close. I believe I'm adaptable and capable of
taking on new challenges and can quickly start to contribute to the DRAM
engineering group if given an opportunity to do so.

While attending BSU I was a mechanical engineering intern working for
Western Aircraft, a relatively small upgrade and repair facility for
private aircraft within the Treasure Valley $($you may have seen their
refueling trucks at the Boise airport$)$. I was responsible for
adding and replacing suites of avionics while verifying no regression in
design occurred. This was all achieved using SolidWorks. I grew to
appreciate the amount of responsibility I was given and learned to
embrace what I didn't know. It motivated me to not only learn on my own
but to not be afraid to collaborate when I came to an impasse.

After earning my Bachelor of Science in Mechanical Engineering from
Boise State University in 2020 I was hired by Raytheon Intelligence \&
Space. Since then I've been primarily focused
on system level integration, verification, and testing of space oriented programs
and have recently taken on the role of Scrum Master.

Thank you for taking the time to review my application. I look forward
to hopefully meeting with you in the future to further discuss my
qualifications for a position as a DRAM Cloud Systems Engineer at Micron Technology.
If you have any questions, please feel free to
email me at \href{mailto:willelsdon@gmail.com}{willelsdon@gmail.com} or
call me at \href{tel:+1-909-202-3855}{909-202-3855}.

Sincerely,

\vspace{0.05in}

Willem Elsdon

\end{document}